At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.

### 2019-11-25 manuscript/reply_to_referees_2.tex

{\Large \bf Reply to Referee 4}

	\begin{refquote}
		Understanding what drives the structure of networks of interactions is key to predict the structure of plant-insect communities (e.g., for conservation or restoration purposes, or to support benefit organisms in agriculture).
		The present study focuses on the contribution of the evolutionary history to the interaction structure, and makes a significant contribution to the understanding of the variability of the phylogenetic signal in plant-insect networks. Here, the strength of the phylogenetic signal is actually quantified while it usually relies on correlation scores, and the effect of plant composition and the identity of plant families are examined to assess whether they could explain the variability of trends described in the literature.
		The dense writing turns out to be a double-edge sword: a lot of information on drivers of phylogenetic signals is compiled in here, but the text is sometime hard to follow. Hence, my following comments mostly pertains to the form, and I trust the authors should be able to address them fairly easily.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript. We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose. Below, we respond to each comment in detail (preceded by \textbf{R:}). We are confident that revising the manuscript in response to the Referee's comments has improved the manuscript.

1. Confusion about description of two dependent variables in analyses [[done]]

@@

		\smallskip

		p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?

	\end{refquote}

	\textbf{R:} The number of shared and unshared interactions are both dependent variables included in the analysis. The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is. The binomial process incorportates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions. We thank the Referee for pointing out text in the introduction which clarifiedthe purpose of including unshared interactions. We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.

	lines XX-XX:

	    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
	    partners ($M_{ij}$) and the number of interaction partners which are not
	    shared ($U_{ij}$). The number of unshared interaction 
	    partners gives valuable information about cases where, for example, 
	    closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.

@@

	\textbf{R:} We agree with the Referee about the difficulty of describing this procedure. We have added an extra line to further explain the logic behind the second round of permutations and hope that this will clarify the goal of these analyses. We have also added a reference to Supplementary Information 3 and thank the Referee for pointing out the oversight.

	Lines XX-XX:

	\begin{quotation}
		This permutation approach also allows us to estimate type I and type II 
	    error for our analysis. Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
	\end{quotation}

5. Suggestion to consider phylogenetic diversity instead of number of plant pairs [[done]]

@@

	\begin{refquote}
		* Testing the effect of network size on the existence of a phylogenetic signal
		Here, it is specifically the number of plant pairs that is studied. I wonder whether the phylogenetic diversity of plants would not be more adapted here. Is it overlooked because similar among networks?
		I think knowing more about this effect would further illuminate why the strength of the phylogenetic signal varies between networks and would be complementary to the analysis testing the effect of plant community composition.
	\end{refquote}

	\textbf{R:} We agree that phylogenetic diversity would be another option for quantifying the 'size' of these networks. However, defining the phylogenetic diversity of each network would depend strongly upon the correctness of of base tree. As we discuss in the methods, our estimates for non-angiosperms are likely to be fairly rough, and some other species are also only approximately dated. Because of this, and because this analysis would more compliment our community-composition analysis than introduce new material, we have opted no to pursue phylogenetic diversity in this manuscript. Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure. This did not appear to be a major issue for our analyses.

### 2019-11-25 manuscript/phylogenetic_signal_manuscript.tex
more corrections. Nearly done with R4

    We calculated niche overlap for each pair of plants $i$ and $j$ by 
    combining the number of shared interaction
    partners ($M_{ij}$) and the number of interaction partners which are not
    shared ($U_{ij}$) into a Jaccard index ($J_{ij}$) describing 
    the proportion of shared interactions. Importantly, we do this while 
    preserving the amount of information provided by each pair of plants
    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
    %
    \begin{equation}
      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
    \end{equation}
    %
    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
    %
    \begin{equation}
      J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
    \end{equation}
    %
    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
    dependent variable rather than the single value $J_{ij}$. Using this tuple form
    allows us to give more 
    weight to species sharing a large number of interaction partners as well as 
    those sharing a large proportion (i.e., to emphasise pairs of generalists 
    sharing most of their interaction partners over specialists sharing a single 
    interaction partner). Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large. % Added because Josh got confused about the distinction.

>>>>

    We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared interaction
    partners ($M_{ij}$) and the number of interaction partners which are not
    shared ($U_{ij}$). The number of unshared interaction 
    partners gives valuable information about cases where, for example, 
    closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. The number of shared and unshared interaction partners together indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of specialists with one common interaction partner.

    We combined the numbers ofshared and unshared interaction partners
    into a Jaccard index ($J_{ij}$) describing 
    the proportion of shared interactions. Importantly, we do this while 
    preserving the amount of information provided by each pair of plants
    (indicated by their numbers of interaction partners). $J_{ij}$ is usually defined as: 
    %
    \begin{equation}
      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
    \end{equation}
    %
    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
    \emph{partners} for species $i$ and $j$ respectively. $J_{ij}$ can also be defined:
    %
    \begin{equation}
      J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
    \end{equation}
    %
    since $U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$. This second definition more closely
    relates to our methodology, which used the tuple ($M_{ij}$, $U_{ij}$) as the
    dependent variable rather than the single value $J_{ij}$. Using this tuple form
    allows us to give more 
    weight to species sharing a large number of interaction partners as well as 
    those sharing a large proportion (i.e., to emphasise pairs of generalists 
    sharing most of their interaction partners over specialists sharing a single 
    interaction partner). Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large. % Added because Josh got confused about the distinction.
